Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-14 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (2)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{resposta} 
Here it is worth to mention that our options about specialized off-the-shelf tools were reduced. As informed at Section 2.1 of the paper, only Hybrid2 and HOMER Pro perform off-grid with battery analysis of PV systems. Hybrid2 is not supported anymore, being in disuse. This information was updated to the paper. Therefore, at this particular kind of system (stand-alone solar PV systems), only HOMER Pro could be used for comparative. Nevertheless, some general use simulation could be used, with the same mathematical model adopted by the automated verification tool. Because of that, we included a mention to that issue in the section 5.4 (Threats to Validity).

Model checking and software simulation are two different techniques that uses mathematical models. However how they work is completely different. Simulation depends on the choice of input variables (and their values) in order to obtain the output. In the other hand, model checking performs an automatic output search that causes the system to fails (a not expected behavior of the system) and presents the input that causes it. Therefore with model checking we can prove the absence of system flaws. This information was included at the revised text as well.

Model checking explores more efficiently the design-space because the specification of the system is based on formal notation (that is converted to Boolean algebra) and the evaluation of variables is made automatically based on constraints (basically system information and electrical load demand transformed in software code) and properties (use defined demands, weather variables that the use do not have precise forecasting). This resulting mathematical model pass through a exploration of its possible states in order to find a configuration where occurs or not a fail. Logically, depending on the number of variables, the number of states explode and is time-consuming during computing of the result.

However, the authors showed in 2016\footnote{Trindade, A.B. and Cordeiro, Applying SMT-based verification to hardware/software partitioning in embedded systems. Des Autom Embed Syst (2016) 20: 1. https://doi.org/10.1007/s10617-015-9163-z} that model checking can present better performance than simulation software when performing hardware-software partitioning in specifically amount of instances.

>>>>

\begin{resposta} 
Note that our options about specialized off-the-shelf tools to design stand-alone solar PV systems are very limited in literature, which motivated us to perform further studies in this area. In particular, as described in Section 2.1, only Hybrid2 and HOMER Pro perform off-grid with battery analysis of PV systems. Hybrid2 is not supported anymore, thereby being in disuse. We have updated this information in our manuscript. Therefore, in this particular research field (stand-alone solar PV systems), only HOMER Pro could be used for comparative purposes. However, in our experiments we could some general simulation tools with the same mathematical model adopted by the automated verification tool. However, this would represent an unfair comparison since we would need to tweak the simulation tools to prepare them for comparison purposes. We have described this limitation in Section 5.4 (``Threats to Validity'') in order to state that additional comparisons could be carried out with general simulation tools if they employ similar mathematical models as the ones described here.

Note that model checking and software simulations are two different techniques that use mathematical models. However, the way they work is completely different. On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output. On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property. In the latter case, if the property is violated (an unexpected behavior of the system), then a model checker presents the input that causes such a violation. Therefore, we can prove the absence of system flaws using model checking. This information was included in the revised version of our manuscript in Section X \textcolor{red}{could you please describe the section here?}.

Importantly, model checking explores more efficiently the design-space because the system specification is based on a formal notation, which gets converted into Boolean algebra; the evaluation of variables is made automatically by a Boolean Satisfiability (SAT) solver based on the system's constraints, i.e., system information and electrical load demand transformed into properties (e.g., use defined demands and non-deterministic weather variables that do not have precise forecasting). This resulting mathematical model is submitted to full exploration of all possible states to find a configuration, where an error might occur or not. Logically, depending on the number of variables, state-explosion can occur and the model checking process might be time-consuming to transverse the entire state-space.

However, the authors demonstrated in $2016$ [1] that model checking can present better performance than software simulation if one performs hardware-software partitioning in specifically amount of instances.

[1] Trindade, A.B. and Cordeiro, Applying SMT-based verification to hardware/software partitioning in embedded systems. Des Autom Embed Syst (2016) 20: 1. https://doi.org/10.1007/s10617-015-9163-z
